### 2017-07-07 pkg/Pmisc/inst/docs/slides.Rmd
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/diseasemapping@1770 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

# hook for multicolumn plots
knitr::knit_hooks$set(plot=hook_plot_beamer)

# hook for smaller plot margins
knitr::knit_hooks$set(
	marginsp = function(before, options, envir){	
		if(!before) return()
		par(mar=c(1.5+0.9*options$marginsp,
				1.5+0.9*options$marginsp,0.2,0.2),
				mgp=c(1.45, 0.45, 0),cex=1.25)
	}		
)

@@

# default chunk options
knitr::opts_chunk$set(echo=FALSE, prompt=TRUE, comment=NA,
		dev='pdf', marginsp=1, fig.start='#',
		fig.width=8, fig.height=4.5, half=NULL,
		tidy=TRUE,tidy.opts=list(indent=2, width.cutoff=55)
)

>>>>

# hook for multicolumn plots
knitr::knit_hooks$set(Pmisc::plot=hook_plot_beamer)

# hook for smaller plot margins
knitr::knit_hooks$set(
	margins = Pmisc::hook_plot_margins
)

@@

# default chunk options
knitr::opts_chunk$set(echo=FALSE, prompt=TRUE, comment=NA,
		dev='pdf', margins=1, fig.start='#',
		fig.width=8, fig.height=4.5, half=NULL,
		tidy=TRUE,tidy.opts=list(indent=2, width.cutoff=55)
)
